\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-03 paper.tex
small position cane in 5.3
updated api image

\item Saccades and transitions: Two fixations are connected by a saccade. Saccades are the sudden variations in the eye-movements. There are two main ways to analyse saccades: 1) saccade lengths are indicative of the amount of change in the attention; and 2) the two ends of a saccade denote a transition between two areas of scene/screen.

@@

\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot). These AOIs are usually based on the hypotheses of the experiment. For example, if in a usability study of a phone advertisement \footnote{http://eyetracking.com.ua/eng/visualization/12.html} (Figure \ref{aoi}) the screen can divided into the advertisement model, the object and the caption. Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.

\begin{figure}
    \centering
    \includegraphics[width=0.4\linewidth]{nokia.jpg}
    \caption{Example of dividing a screen in Areas of interest. Source: http://eyetracking.com.ua/eng/visualization/12.html}
    \label{aoi}
\end{figure}

@@

\subsection{Participants}

>>>>

\item Saccades and transitions: Two fixations are connected by a saccade. Saccades are the sudden variations in the eye-movements (Figure \ref{aoi}). There are two main ways to analyse saccades: 1) saccade lengths are indicative of the amount of change in the attention; and 2) the two ends of a saccade denote a transition between two areas of scene/screen .

@@

\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot). These AOIs are usually based on the hypotheses of the experiment. For example, if in a usability study of a phone advertisement (Figure \ref{aoi}) the screen can divided into the advertisement model, the object and the caption. Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{scanpathVars}
    \caption{Example of dividing a screen in Areas of interest and the saccades 
    (lines). Source: \cite{sharma2014how}}
    \label{aoi}
\end{figure}

@@

\vspace{1cm}
\subsection{Participants}
